---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

--- title: "Simulate Two Correlated Random Variables" author: "Zishu Zhu" date: "September 26, 2020" output: pdf_document: default html_document: default --- ## I. Introduction I have surveyed all of the 347 students in sta 032 class and collected 10 adults' forearm length and height. My response variable is forearm length and explanatory variable is height. ## II. Exploratory Data Analysis ```{r, include=FALSE} library(tidyverse) ```

```{r, include=FALSE} 
id <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10) #ids of our sample data height <- c(165, 158, 160, 166, 178, 166.5, 163, 179, 187, 165) #heights from our sample data forearm <- c(25, 23, 23, 23.5, 28, 24, 23.5, 29, 24, 26) #forearms from our sample data the_data <- cbind(id, height, forearm) #bind all of the collected data together by coloumn the_data <- as.data.frame(the_data) #build a dataframe of out data set the_data 
```

```{r, echo = FALSE}
scat.plot <- ggplot(the_data, aes(x = height, y = forearm))+ geom_point()+ labs(x = "Height", y = "Forearm Length", title = "Scatter Plot of Height vs. Forearm Length 7813") # scatter plot which can help us analyzing the relationship between these two variables scat.plot 
```
```{r, echo = FALSE}
my.data <- data.frame("values"=c(height, forearm), "variables"=c(rep('height', 10), rep('forearm', 10))) box.plot <- ggplot(data=my.data, aes(y=values, x=variables))+ geom_boxplot()+ labs(title = "Box Plot of Height vs. Forearm Length 7813") #I draw a boxplot for my sample data to see the dispersion of the data. box.plot 
```

```{r, echo = FALSE}
hist.plot <- ggplot(the_data, aes(x = forearm, y = ..count..))+ geom_histogram(binwidth = 1, color = "white")+ labs(x = "Forearm Length", y = "Frequncy", title = "Histogram of Forearm Length 7813") #Histogram help to see the distribution of random variable Forearm Length hist.plot 

```

I have drawed three plots above. The first one is a scatter plot of Height vs. Forearm Length. There is a weak linear association between height and forearm length. Because is only ten sample points on the plot, I cannot say that these two variables can form a linear association. The second graph is a boxplot which is used to analyze the variability of the sample data. The middle 50% of values for height is from 163.5cm to 175.125cm. The middle 50% of values for forearm is from 23.5cm to 25.75cm. And from the box plot we can see that both of the reponse variable "forearm", and predictor variable "height" are right skewed. There is no outlier for both variables. The histogram is a right skewed histogram and it is asymmetrical. The histogram is not bell-shaped. From the histogram, we can see that my response variable "Forearm Length" is not approximately normal distributed. $Centre$ 
  
```{r, echo = FALSE}
for_median <- median(the_data$forearm) hei_median <- median(the_data$height) for_mean <- mean(the_data$forearm) hei_mean <- mean(the_data$height) 
```

The centre of the sample data is as follow. The mean forearm length of the sample data is `r for_mean`cm and the median forearm length of the sample data is `r for_median`cm. The mean height of the sample data is `r hei_mean`cm and the median height of the sample data is `r hei_median`cm. $Spread$ 

```{r, echo = FALSE}
for_sd <- sd(the_data$forearm) hei_sd <- sd(the_data$height) for_iqr <- IQR(the_data$forearm) hei_iqr <- IQR(the_data$height) 
``` 

The spread of the sample data is as follow. The standard deviation of forearm length of the sample data is `r for_sd`cm and the IQR of forearm length of the sample data is `r for_iqr`cm. The standard deviation of height of the sample data is `r hei_sd`cm and the IQR of height of the sample data is `r hei_iqr`cm. $Unusual$ $points$ 

```{r, include=FALSE} 
upwhisk_for <- quantile(the_data$forearm, 0.75)+1.5*for_iqr which(the_data$forearm > upwhisk_for) lowwhisk_for <- quantile(the_data$forearm, 0.25)-1.5*for_iqr which(the_data$forearm < lowwhisk_for) ``` 


```{r, include=FALSE}
upwhisk_hei <- quantile(the_data$height, 0.75)+1.5*hei_iqr which(the_data$height > upwhisk_hei) lowwhisk_hei <- quantile(the_data$height, 0.25)-1.5*hei_iqr which(the_data$height < lowwhisk_hei) ```

There is no outlier or unusual point for either response variable height of the sample data or predictor variable forearm of the sample data. ## III. Methods and Model 

```{r, echo = FALSE}
mymod <- lm(forearm~height, data = the_data) ```

```{r, echo = FALSE}
summary(mymod) ```

$\bullet$ From the summary of the linear model. $b_{0}=3.36881$ and $b_{1}=0.12759$. The fitted linear model is $\hat{y_{i}}=3.36881+0.12759 \cdot x_{i}$. $\hat{y_{i}}$ stands for the expected forearm length and $x_{i}$ stands for the height. $\bullet$ By looking at the p-value for intercept $\beta_{0}$ is 0.7704 and it is larger than 0.05. We should not reject the null hypothesis that $\beta_{0}=0$ at 5% significance level. Therefore, $\beta_{0}$ is not statistically different from zero. And the p-value for slope $\beta_{1}$ is 0.0894 and it is also larger than 0.05. Thus, we should not reject the null hypothesis that $\beta_{1}=0$ at 5% significance level. So $\beta_{1}$ is also not statistically different from zero. $\bullet$ $b_{0}=3.36881$ means that the expected forearm length is 3.36881 cm when the height is 0 cm. $b_{1}=0.12759$ means that when the height is increased by 1 cm, the expected forearm length will increase by 0.12759 cm. 

## IV. Discussions and Limitations 

```{r, echo = FALSE}
mod.resi <- tibble(res = mymod$residuals, fit = mymod$fitted.values) res.fitted <- ggplot(mod.resi)+ geom_point(aes(x=fit, y=res))+ geom_hline(yintercept = 0, lty = 2, color = "red")+ labs(x = "fitted values", y = "residuals", title = "residual against fitted value 7813") res.fitted ``` 


$\bullet$ One of the potential lurking variable is hand length. The limitation of my fit is that from the graph of residual against fitted value, we can find that the sample data has non-constant variance(increasing variance). $\bullet$ The distance and speed of a car is driving is another pair of variables. The response variable is distance.